Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-13 Publications/2013-IPMI/Latex/02-Abstract.tex
New Abstract (v.3.0)

\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract.
%\dots
%\keywords{diffusion weighted imaging, connectomics, echo planar imaging, magnetic resonance, segmentation, registration, distortion correction}
\end{abstract}

>>>>

Whole-brain connectivity analysis on diffusion weighted MR images (DWI) involves
a large set of processing techniques. Particularly, an accurate white matter (WM)
segmentation is required, with precise location of the interface with grey matter.
High-standard segmentation and surface parcellations are readily available on 
anatomical images, such as T1-weighted MRI. However DWI typically have drastically 
lower resolution, and generally exhibit important distortions. Here, we propose a 
segmentation-registration framework that exploits the detailed anatomy extracted 
from anatomical MRI as reference shape-prior for DWI segmentation. We use the 
active contours without edges model to look for a deformation field that optimally 
maps the shape prior on the multivariate features in diffusion space. This joint
approach attends the intrinsic coupling of segmentation, parcellation, and distortion 
correction problems to finally obtain reliable connectivity networks. Preliminary
results on synthetic datasets and simulated DWI confirm the effectiveness of our 
approach.
